Monitoring and Projecting Global Hunger

### 2020-11-18 docs/modeling_fies.tex
Fix errors in overleaf and change title

\title{A Global Picture of Hunger}

@@

\section{Results}
\subsection{Food Insecurity over Time}
Globally, in the year 2020, we estimate that 820 million people are above the threshold for severe food insecurity, and 2.5 billion people are above the threshold for moderate food insecurity (See Fig. \ref{fig:timeseries}). These numbers are higher than the estimates in the 2020 FAO State of Food Insecurity report, which reports about 746 million severely food insecure people and 2 billion people experiencing at least moderate food insecurity in 2019 \ref{sofi2020}.

@@

For severe food insecurity, the most important variable for predicting food security levels is the Poverty Headcount Index, followed by the rate of stunting.  For predicting the rate of people with at least moderate food insecurity, GDP per capita is the most important, followed closely by the Poverty Headcount Index.  For the rate of severe food insecurity, the country's Gini coefficient was more important compared to moderate food insecurity.  Across both indicators, economic variables were the most relevant predictors.

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{img/VIMP.pdf}
  \caption{Importance of each variable in predicting the percent of a population over thresholds for moderate and severe food insecurity.  This is determined by the increase in the error when the variable is permuted before fitting the model.}
  \label{fig:map}
\end{figure}

@@

\section

>>>>

\title{Monitoring and Projecting Global Hunger}

@@

\section{Results}
\subsection{Food Insecurity over Time}
Globally, in the year 2020, we estimate that 820 million people are above the threshold for severe food insecurity, and 2.5 billion people are above the threshold for moderate food insecurity (See Fig. \ref{fig:timeseries}). These numbers are higher than the estimates in the 2020 FAO State of Food Insecurity report, which reports about 746 million severely food insecure people and 2 billion people experiencing at least moderate food insecurity in 2019 \citep{sofi2020}.

@@

For severe food insecurity, the most important variable for predicting food security levels is the Poverty Headcount Index (See Fig. \ref{fig:vimp}, followed by the rate of stunting.  For predicting the rate of people with at least moderate food insecurity, GDP per capita is the most important, followed closely by the Poverty Headcount Index.  For the rate of severe food insecurity, the country's Gini coefficient was more important compared to moderate food insecurity.  Across both indicators, economic variables were the most relevant predictors.

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{img/VIMP.pdf}
  \caption{Importance of each variable in predicting the percent of a population over thresholds for moderate and severe food insecurity.  This is determined by the increase in the error when the variable is permuted before fitting the model.}
  \label{fig:vimp}
\end{figure}

@@

### 2020-11-18 docs/modeling_fies_supplement.tex
Fix errors in overleaf and change title

\pagestyle{fancy}
\fancyhf{}
\lfoot{Supplemental Materials for \textit{A Global Picture of Hunger}}
\rfoot{\thepage}

@@

\begin{center}
\section*{Supplemental Info for \textit{A Global Picture of Hunger}}
\end{center}
\setcounter{table}{0}
\setcounter{figure}{0}
\setcounter{section}{0}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thesection}{S\arabic{section}}

@@

\pagebreak
\subsection{Topographic Ruggedness}
As a measure of accessibility, our models include the mean topographic ruggedness of each subnational area as a covariate. We obtain the variable using a gridded dataset of elevation from the USGS \citep{USGS1996} and calculate the index at each grid cell using the methodology from Riley et al. \citep{Riely1999}. We then aggregate the values for all the grid cells within each administrative area. The variable is constant in the estimation and projection period.

>>>>

\pagestyle{fancy}
\fancyhf{}
\lfoot{Supplemental Materials for \textit{Monitoring and Projecting Global Hunger}}
\rfoot{\thepage}

@@

\begin{center}
\section*{Supplemental Materials for \textit{Monitoring and Projecting Global Hunger}}
\end{center}
\setcounter{table}{0}
\setcounter{figure}{0}
\setcounter{section}{0}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thesection}{S\arabic{section}}

@@

\pagebreak
\subsection{Topographic Ruggedness}
As a measure of accessibility, our models include the mean topographic ruggedness of each subnational area as a covariate. We obtain the variable using a gridded dataset of elevation from the USGS \citep{USGS1996} and calculate the index at each grid cell using the methodology from Riley et al. \citep{Riley1999}. We then aggregate the values for all the grid cells within each administrative area. The variable is constant in the estimation and projection period.
